Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-21 paper.qmd
Updated Figure 9 (e)

```{r}
#| label: distribution-scurve
## To initialize effective bins along x
effective_bin1_scurve <- 11

@@

mse_scurve_lwd2 <- error_rm_scurve |>
  filter(b_non_empty >= 5) |>
  ggplot(aes(x = b_non_empty,y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("m (b1 = 11)") + 
  ylab("MSE") +
  ggtitle("(e)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

>>>>

```{r}
#| label: distribution-scurve
## To initialize effective bins along x
effective_bin1_scurve <- 14

@@

mse_scurve_lwd2 <- error_rm_scurve |>
  filter(b_non_empty >= 5) |>
  ggplot(aes(x = b_non_empty,y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("m (b1 = 14)") + 
  ylab("MSE") +
  ggtitle("(e)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```
